Work Fragmentation in Developer Interaction Data

### 2015-12-18 paper.tex
Minor changes

\subsection{The Eclipse UDC}
The Usage Data Collector (UDC) dataset is a large compendium of information about interaction data from users of Eclipse, collected from December 2008 to August 2010, with the intention to keep track of how programmers are using the IDE. The framework listens to the events triggered by the user or the system, such as: edition and navigation commands; the startup of a plug in; or the closing of the platform. To be more specific, UDC collects information about loaded bundles, commands accessed via keyboard shortcuts, actions invoked via menu or tool-bars, perspective changes, view usage and editor usage. The UDC is a large dataset that contains information of around 1,800,000 users, and has a total of 2,323,233,101 unique rows with 5 attributes each. Table \ref{tbl:att_udc} shows a description of the attributes.

@@

\subsection{Selection and transformation}
We used the pre-processed data by Murphy-Hill, that is published on Google BigQuery \cite{SnipesETALASD}. This is an alternative version of the original UDC dataset, that is cleaned and preprocessed, so that the transformation phase is simple and focused on our needs. Due to the magnitude of the dataset we only worked on a fragment of it. We took a random sample of 1,000 users that is larger than the dataset we were able to obtain for the Mylyn study.

@@

Once the events were classified and sorted, we split the dataset into sessions, defining a session as a period of registered work between interruptions of 8 hours or larger, as we did with Mylyn. We split the data by users to avoid a conflict between the last event of a user and the first one of another. After this, we obtained a total of 28,989 different sessions; but after a filter to keep only those with at least 30 minutes of productive time (as we did with the Mylyn dataset), we ended up with 15,825 useful sessions, in contrast with the 4,284 we had from Mylyn. Some statistics about the sessions can be seen in the Table \ref{tbl:stats_sessions_udc}, and a histogram of the duration of the sessions on UDC is shown in the Figure \ref{fig:hist_session_duration_udc}, which ignores outliers by setting a threshold of three times the standard deviation.

>>>>

\subsection{The Eclipse UDC}
The Usage Data Collector (UDC) dataset is a large compendium of information about interaction data from users of Eclipse, collected from December 2008 to August 2010, with the intention to keep track of how programmers are using the IDE. The framework listens to the events triggered by the user or the system, such as: edition and navigation commands; the startup of a plug in; or the closing of the platform. To be more specific, UDC collects information about loaded bundles, commands accessed via keyboard shortcuts, actions invoked via menu or tool-bars, perspective changes, view usage and editor usage. The UDC is a large dataset that contains information of around 1,800,000 users, and has a total of 2,323,233,101 unique rows with 5 attributes each. The Table \ref{tbl:att_udc} shows a description of the attributes.

@@

\subsection{Selection and transformation}
We used the preprocessed version of the data that is published on Google BigQuery, by Murphy-Hill \cite{SnipesETALASD}. This is an alternative version of the original UDC dataset, that is cleaned and preprocessed, so that the transformation phase is simple and focused on our needs. Due to the magnitude of the dataset we only worked on a fragment of it. We took a random sample of 1,000 users that is larger than the dataset we were able to obtain for the Mylyn study.

@@

Once the events were classified and sorted we split the dataset into sessions, defining a session as a period of registered work between interruptions of 8 hours or larger, as we did with Mylyn. We split the data by users to avoid a conflict between the last event of a user and the first one of another. After this, we obtained a total of 28,989 different sessions; but after a filter to keep only those with at least 30 minutes of productive time (as we did with the Mylyn dataset), we ended up with 15,825 useful sessions, in contrast with the 4,284 we had from Mylyn. Some statistics about the sessions can be seen in the Table \ref{tbl:stats_sessions_udc}, and a histogram of the duration of the sessions on UDC is shown in the Figure \ref{fig:hist_session_duration_udc}, which ignores outliers by setting a threshold of three times the standard deviation.
